The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2017-03-23 article/unrave.tex
'Upgrade' to aastex v6.1

\documentclass[preprint]{aastex}

@@

\author{
Andrew~R.~Casey\altaffilmark{1},
Keith~Hawkins\altaffilmark{1},
David~W.~Hogg\altaffilmark{2,3,4,5},
Melissa~Ness\altaffilmark{5},
Hans~Walter-Rix\altaffilmark{5},
Georges~Kordopatis\altaffilmark{6},
Andrea~Kunder\altaffilmark{6,7},
Matthias~Steinmetz\altaffilmark{6},
Sergey~Koposov\altaffilmark{1},
Harry~Enke\altaffilmark{6},
Jason~Sanders\altaffilmark{1},
Gerry~Gilmore\altaffilmark{1},
Toma\v{z}~Zwitter\altaffilmark{8},
Kenneth~C.~Freeman\altaffilmark{9},
Luca~Casagrande\altaffilmark{9},
Gal~Matijevi\v{c}\altaffilmark{8},
George~Seabroke\altaffilmark{10},
Olivier~Bienaym\'e\altaffilmark{11},
Joss~Bland-Hawthorn\altaffilmark{12},
Brad~K.~Gibson\altaffilmark{13},
Eva~K.~Grebel\altaffilmark{14},
Amina~Helmi\altaffilmark{15},
Ulisse~Munari\altaffilmark{16},
Julio~F.~Navarro\altaffilmark{17,18},
Warren~Reid\altaffilmark{19,20},
Arnaud~Siebert\altaffilmark{11},
Rosemary~Wyse\altaffilmark{21}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}

@@

\keywords{stars: fundamental parameters --- stars: abundances
% Clear rest of page
\clearpage}

@@

\acknowledgements
We thank 
	Borja Anguiano (Macquarie),
	Jonathan Bird (Vanderbilt),
	Sven Buder (MPIA), 
	Sofia Randich (INAF),
and
	Kevin Schlaufman (Carnegie Observatories).
This research made use of: 
  	NASA's Astrophysics Data System Bibliographic Services;
  	Astropy, a community-developed core Python package for Astronomy \citep{astropy};
and 
  	\project{TOPCAT} \citep{Taylor_2005}.
This work was partly supported by the European Union FP7 programme through ERC 
grant number 320360. A.~R.~C. thanks King's College of the University of Cambridge
for their support.  Funding for K.~H.~ has been provided through the Simons 
Foundation Society of Fellows and the Marshall Scholarship.
Funding for RAVE has been provided by: the Australian Astronomical Observatory; 
the Leibniz-Institut fuer Astrophysik Potsdam (AIP); the Australian National 
University; the Australian Research Council; the French National Research Agency;
the German Research Foundation (SPP 1177 and SFB 881); the European Research 
Council (ERC-StG 240271 Galactica); the Istituto Nazionale di Astrofisica at 
Padova; The Johns Hopkins University; the National Science Foundation of the USA
(AST-0908326); the W. M. Keck foundation; the Macquarie University; the 
Netherlands Research School for Astronomy; the Natural Sciences and Engineering 
Research Council of Canada; the Slovenian Research Agency (research core funding 
No. P1-0188); the Swiss National Science Foundation; the Science \& Technology 
Facilities Council of the UK; Opticon; Strasbourg Observatory; and the 
Universities of Groningen, Heidelberg and Sydney. The RAVE web site is 
https://www.rave-survey.org.

@@

% A magic, bad, hack.
\noindent{}$^{1}${Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK} \\
$^{2}${Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA} \\
$^{3}${Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA} \\
$^{4}${Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA} \\
$^{5}${Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany} \\
$^{6}${Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany} \\
$^{7}${Saint Martin's University, Old Main, 5000 Abbey Way SE, Lacey, WA 98503, USA} \\
$^{8}${University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia} \\
$^{9}${Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia} \\
$^{10}${Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK} \\
$^{11}${Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France} \\
$^{12}${Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia} \\
$^{13}${E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom} \\
$^{14}${Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany} \\
$^{15}${Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands} \\
$^{16}${INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy} \\
$^{17}${Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2} \\
$^{18}${Senior CIfAR Fellow} \\
$^{19}${Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia} \\
$^{20}${Western Sydney University, Penrith South DC, NSW 1797} \\
$^{21}${Johns Hopkins University, Baltimore, MD, USA} \\

>>>>

\documentclass[preprint]{aastex61}

@@

\author{Andrew~R.~Casey}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{Keith~Hawkins}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{David~W.~Hogg}
\affiliation{Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\author{Melissa~Ness}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\author{Hans-Walter~Rix}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\author{Georges~Kordopatis}
\affiliation{Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany}

\author{Andrea~Kunder}
\affiliation{Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany}
\affiliation{Saint Martin's University, Old Main, 5000 Abbey Way SE, Lacey, WA 98503, USA}

\author{Matthias~Steinmetz}
\affiliation{Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany}

\author{Sergey~Koposov}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{Harry~Enke}
\affiliation{Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany}

\author{Jason~Sanders}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{Gerry~Gilmore}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

\author{Toma\v{z}~Zwitter}
\affiliation{University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia}

\author{Kenneth~C.~Freeman}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia}

\author{Luca~Casagrande}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia}

\author{Gal~Matijevi\v{c}}
\affiliation{University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia}

\author{George~Seabroke}
\affiliation{Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK}

\author{Olivier~Bienaym\'e}
\affiliation{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France}

\author{Joss~Bland-Hawthorn}
\affiliation{Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia}

\author{Brad~K.~Gibson}
\affiliation{E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom}

\author{Eva~K.~Grebel}
\affiliation{Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany}

\author{Amina~Helmi}
\affiliation{Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands}

\author{Ulisse~Munari}
\affiliation{INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy}

\author{Julio~F.~Navarro}
\affiliation{Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2}
\affiliation{Senior CIfAR Fellow}

\author{Warren~Reid}
\affiliation{Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia}
\affiliation{Western Sydney University, Penrith South DC, NSW 1797}

\author{Arnaud~Siebert}
\affiliation{Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France}

\author{Rosemary~Wyse}
\affiliation{Johns Hopkins University, Baltimore, MD, USA}

@@

\keywords{stars: fundamental parameters --- stars: abundances}

@@

\acknowledgements
We thank 
	Borja Anguiano (Macquarie),
	Jonathan Bird (Vanderbilt),
	Sven Buder (MPIA), 
	Sofia Randich (INAF),
and
	Kevin Schlaufman (Carnegie Observatories).

\software{Astropy, \citep{astropy}, \project{TOPCAT} \citep{Taylor_2005}}

This research made use of NASA's Astrophysics Data System Bibliographic Services.
This work was partly supported by the European Union FP7 programme through ERC 
grant number 320360. A.~R.~C. thanks King's College of the University of Cambridge
for their support.  Funding for K.~H.~ has been provided through the Simons 
Foundation Society of Fellows and the Marshall Scholarship.
Funding for RAVE has been provided by: the Australian Astronomical Observatory; 
the Leibniz-Institut fuer Astrophysik Potsdam (AIP); the Australian National 
University; the Australian Research Council; the French National Research Agency;
the German Research Foundation (SPP 1177 and SFB 881); the European Research 
Council (ERC-StG 240271 Galactica); the Istituto Nazionale di Astrofisica at 
Padova; The Johns Hopkins University; the National Science Foundation of the USA
(AST-0908326); the W. M. Keck foundation; the Macquarie University; the 
Netherlands Research School for Astronomy; the Natural Sciences and Engineering 
Research Council of Canada; the Slovenian Research Agency (research core funding 
No. P1-0188); the Swiss National Science Foundation; the Science \& Technology 
Facilities Council of the UK; Opticon; Strasbourg Observatory; and the 
Universities of Groningen, Heidelberg and Sydney. The RAVE web site is 
https://www.rave-survey.org.

@@
